% 
%  mainnumeric.tex
%  Numeric Cases without SMC
%  
%  Created by Sergei Vieira Silva on 2011-05-07.
%  Copyright 2011 Sergei Vieira. All rights reserved.
% 
\documentclass[]{elsarticle}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref} 
\RequirePackage{hypernat}
\usepackage[latin1]{inputenc}     
%\usepackage[applemac]{inputenc}
\usepackage{graphicx}
\usepackage{pdfsync} 
\usepackage{amsmath}   
\usepackage{amssymb}    
\usepackage{cases}
%\usepackage{bbm}    
%\usepackage{amsthm}
%\usepackage{mathrsfs}
\usepackage[T1]{fontenc}
%\usepackage[default]{frcursive} %Esse pacote traz as fontes cursivas.
\usepackage{svn-multi}
\svnidlong
{$LastChangedBy: sergeidesk $}      
{$LastChangedRevision: 18 $} 
{$LastChangedDate: 2011-05-04 14:01:01 -0300 (Wed, 04 May 2011) $} 
{$HeadURL:$}

\newtheorem{theorem}{Theorem}
\newtheorem{assumption}{Assumption}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
%\newtheorem{algorithm}[theorem]{Algorithm}
%\newtheorem{axiom}[theorem]{Axiom}
%\newtheorem{case}[theorem]{Case}
%\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
%\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{corollary}{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}{Definition}
\newtheorem{resumo}{Resumo}
\newtheorem{example}{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}{Lemma}
%\newtheorem{notation}[theorem]{Notation}
\newtheorem{principle}[theorem]{Principle}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{remarkapp}{Remark} 
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}
\newenvironment{proof}[1][Proof]{\textbf{#1} }{\rule{0.5em}{0.5em}}

\begin{document}
\begin{frontmatter}
	\title{Onedimensional Screening without Single-Crossing: Numerical Guided Approach.\footnote{Revision \textit{1.\svnrev}}} 

	\author[I,E]{A. Araujo} 
	%\corauth[cor]{Corresponding author.}
	\ead{aloisio@impa.br}
	\author[I]{S. Vieira}
	%\corauth[cor]{Corresponding author.}
	\ead{srgvie@gmail.com}
        \author[I]{C. Parra}
	%\corauth[cor]{Corresponding author.}
	\ead{carolina.parrama@gmail.com}

	\address[I]{Instituto Nacional de Matemática Pura e Aplicada, Estrada Dona Castorina 110, Rio de Janeiro, Brasil}
	\address[E]{Graduate School of Economics, Getúlio Vargas Foundation, Praia de Botafogo, 190, Rio de Janeiro, Brazil}

\begin{abstract}
In this paper we solve stylized problems in  
onedimensional screening without the single-crossing condition. With the aid of numerical optimization tools, we guess which are the relevant binding incentive compatibility constraints.
 Then we use this information to build a candidate solution that matches the numerical pattern.


\end{abstract}

\vspace{0.7cm}

\begin{keyword}
unidimensional screening, non single-crossing

\vspace{0.2cm}   

\textit{Palavras chaves:} screening unidimensional, no single-crossing.

\smallskip  
  
\textit{JEL Codes: D42, D82.}  
\end{keyword} 
\end{frontmatter}  
\date{}
\newpage
\input{introduction.tex} 
\input{model.tex}
\input{examples.tex}
%\input{conclusion.tex} 
\newpage 
%\appendix
%\input{appendix.tex}

\newpage 
%\bibliographystyle{siam}
%\bibliography{mainnumeric}

\begin{thebibliography}{11}
 \bibitem{Araujo} A. Ara\'ujo, H. Moreira, \emph{Adverse Selection Problems
without the Spence-Mirrlees Condition}. Journal of Economic Theory (Print), v. 145, p. 1113-1141, 2010.

\bibitem{Araujo} A. Ara\'ujo, H. Moreira, S. Vieira \emph{Nonlinear Pricing Beyond the Demand Profile Approach }.

\bibitem{Gibbard} A. Gibbard \emph{Manipulation for voting schemes}. Econometrica, v. 41, p. 587-601, 1973

\bibitem{Guesnerie} R. Guesnerie \emph{On taxation and incentives: further reflections on the limit of redistribution}. Mimeo, 1981.

\bibitem{Hammond} P. Hammond \emph{Straightforward individual incentive compatibility in large economies}. The Review of Economic Studies, v. 46, p. 263-282, 1979..

\bibitem{Jullien} B. Jullien \emph{Participation constraints in adverse selection models }.Journal of Economic Theory, v. 93, p. 1-47, 2000.

\bibitem{Laffont} J. J. Laffont, E. Maskin, J. C. Rochet \emph{Optimal nonlinear pricing with two dimensional characteristics }.Information, Incentives, and Economic Mechanisms: Essays in Honor of Leonid Hurwicz by Theodore Groves, Roy Radner, and Stanley Reiter, 1987.

\bibitem{Maskin} E. Maskin, J. Riley \emph{Monopoly with incomplete information}. RAND Journal of Economics, v. 15, p. 171-196, 1984.

\bibitem{Milgrom} P. Milgrom, I. Segal \emph{Envelope theorems for arbitrary choice sets}. Econometrica, v. 70, p. 583-601, 2002.

\bibitem{Rochet} J. C. Rochet \emph{A necessary and sufficient condition for rationalizability in a quasi-linear context}. Journal of Mathematical Economics, v.16, p.191-200, 1987.

\bibitem{Wilson} R.B. Wilson  \emph{Nonlinear Pricing}. Oxford University Press, 1993.

\end{thebibliography}

\end{document}

